
```{r}
my.dat <- with(anscombe, data.frame(X=x1, y=y1))
my.dat
```

## Population Equation
$y = \beta_0 + \beta_1 X + \eta$


##Null Hypothesis
$\beta_1 = 0$


##Regression
```{r}
fit1 <- lm(y~X, data=my.dat)
library(arm)
display(fit1) 

```
Two coeff: slope and intercept

```{r}
library(ggplot2)
my.dat$e = residuals(fit1)
my.dat$y.hat = fitted(fit1)
qplot(1:nrow(my.dat), y, data=my.dat, main="Time Series - y", xlab="Obs #", ylab="Values")
p <- ggplot(aes(x=X, y=y), data=my.dat) + geom_point(color="steelblue", size=5)
p
```

### Adding regression line
```{r}
p <- p + geom_smooth(method="lm", se=FALSE)
p
```

### Adding fitted values
```{r}
p <- p + geom_point(aes(x=X, y=y.hat), color="firebrick", shape=20, size=5)
p
```

## Analytically...

```{r}
dat2 <- data.frame(y=my.dat$y, X=my.dat$X)

mu.y <- mean(dat2$y)
mu.x <- mean(dat2$X)
mu.x
mu.y

dat2$d.y <- dat2$y - mu.y
dat2$d.X <- dat2$X - mu.x
dat2$d.X.sq <- dat2$d.X^2
dat2$d.Xy <- dat2$d.X * dat2$d.y
head(dat2)

SSD.X.sq <- sum(dat2$d.X.sq)
SSD.Xy <- sum(dat2$d.Xy)

b.1 <- SSD.Xy/SSD.X.sq

```
$b_1 = \frac{Cov[xy]}{Var[x]}$

### What about $b_0$

```{r}
b.0 <- mu.y - b.1*mu.x
b.0

```

### Fitted values and errors

```{r}

dat2$y.hat <- b.0 + b.1*dat2$X
dat2$e <- dat2$y - dat2$y.hat
```

### Sums of Squares, MS, F-Test

```{r}
SSTot <- sum(dat2$d.y^2)
SSRes <- sum(dat2$e^2)
SSReg <- SSTot - SSRes

MSReg <- SSReg/1
MSRes <- SSRes/(nrow(dat2)-2)

F.stat <- MSReg/MSRes
t.stat <- sqrt(F.stat)
F.stat

```

### p-value: probability bigger than the given value
P(X>x) = 1-P(X<x)

```{r}
p.val <- 1-pf(F.stat, 1, 9)
p.val
```


### Coefficient of Determination
What portion of variance does error account for

```{r}
SSRes/SSTot
```
$R^2$ in terms of the residuals
```{r}
R.sq <- 1 - SSRes/SSTot
```
This is equal to cor(dat2$y, dat2$y.hat)^2

### Comparing Results
####Coefficient

```{r}
coef(fit1)
coef(summary(fit1))
c(b.0,b.1, t.stat)
```
####Fitted values
```{r}
round(fitted(fit1) - dat2$y.hat, digits=10)
```

#### F-test
```{r}
anova(fit1)
c(SSReg, SSReg, SSTot)
c(MSReg, MSReg)
F.stat
```





