Lab 3
========================================================


```{r}
library(reshape2)
my.dat <- ChickWeight[,c("weight", "Diet")]
summary(my.dat)
```

#Fixed Effect Model (<-> Random Effect Model)

Whether several groups in a population are different or not.

j: each group, 
i: individual output, 
$\alpha_j$: difference of the group from the grand mean,
a: the number of groups,
$\mu_j$: mean of each group

- Greek letters: all about POPULATION
- Null Hypothesis: $\alpha_j = 0$, where $j=1,2,...$
- Error: N(0, $\sigma^2$)
- Regression Model

#ANOVA

- F = $\frac{MS_{between}}{MS_{within}}$
- $SS_B$: $\sum (n_j(Y_{.j} - Y_{..})^2$

```{r}
gm <- mean(my.dat$weight)
a <- aggregate(weight~Diet, dat=my.dat, mean)
names(a) <- c("Diet", "mean.j")
a$hat <- a$mean.j-gm
a$n <- table(my.dat$Diet)
SSB <- sum(a$hat^2*a$n)
```

Their weights and their groups mean

- $SS_W = \sum\sum(Y_ij - Y_{.j})^2$ 

```{r}
SSW <- sum(apply(my.dat, 1, function(x)
  (a[a$Diet==x['Diet'],]$mean.j - 
  as.numeric(x['weight']))^2 ))  
```

- $df_B = a - 1$
- $df_W = N - a$

```{r}
df.B <- length(levels(my.dat$Diet)) - 1 
df.W <- nrow(my.dat) - df.B - 1
```

- levels: how many different variables in the parameter 


- Mean Squares
```{r}
MSB <- SSB/df.B
MSW <- SSW/df.W
F.stat <- MSB/MSW
```

- F value assumes F distribution: has 2 parameteres ($df_B$, $df_W$)
- p value? Probability $P(T>t | H_0)$

```{r}
p.level = 1-pf(F.stat, df.B, df.W)
p.level
```

- c function: combine
##### Compare the result!
```{r}
c(F=F.stat, p=p.level)

fit1 <- lm(weight~Diet, my.dat)
anova(fit1)
```


####Cumulative Probability Function $\Phi$

- $\Phi(0) = 0.5$
- if we do pf(F, df, df), it shows cdf, so we should substract it from 1.

#Bonferroni Correction

- $P(T\geq t_i|H_0) \leq \frac{\alpha}{n}, i=1 ... n$
- $P(T\geq t_i|H_0)n \leq \alpha, i=1 ... n$
- Multiply p value by n and compare it with $\alpha$. 

#### Uncorrected pairwise comparisons
```{r}
mc.none <- with(my.dat,
                pairwise.t.test(weight, Diet, p.adj="none"))
mc.none
```

- Banferroni adjustment
```{r}
mc.bonf <- with(my.dat,
                pairwise.t.test(weight, Diet, p.adj="bonf"))
mc.bonf
```

- 1,3 and 1,4 are significant
- Number of comparisons = k(k-1)/2

##### Compare the result with the actual producted value
```{r}
k <- length(levels(my.dat$Diet))
n.c <- k*(k-1)/2
n.c
mc.none$p.value <- mc.none$p.value*n.c
mc.none
```

