Lab 4
========================================================

# ANOVA, t-test, and Regression (Overview)

- An example of MOM_Highschool vs. Child's IQ
- R-squared: % of variance
- t-test? two groups are not overlapping -- it's significant!
- Regression? drawing a line.
- Interactions between categorical (mom high) vs. continuous (mom IQ)
  - One more term is added: mom_hs X mom_iq  
  - All you can say with this interaction term is that two slopes are different.
  

- Assumptions and diagnostics (in order of importance)
  - Validity
  - Additivity and Linearity
  - Independence of errors
  - Equal variance or errors
  - Normality of errors

# ANOVA Stuff II

## Fixed versus Random
- $Y_{ij}$: Weight for every chicken.
- $\mu$: population mean
- $Y_{ij} \sim N(\mu, \sigma^2)$: the model is an interpretation of this distribution.
- Models are same.
- Difference?
  - Research question: Does this matter? vs. What affects the result?
  - What we are doing about error term.
  - Variable's are random variable vs. fixed variable

```{r}
mydat <- ChickWeight
head(mydat)
fit1 <- weight~Diet
summary(aov(fit1, mydat))

```

- aov fundtion is another way of doing ANOVA
- 1 - (F value, df_between, df_within) 

## Random?
```{r}
fit2 <- weight~Error(Diet)
summary(aov(fit2, mydat))
```


- 1 is the grand mean (just put there)
```{r}
fit3 <- weight~Diet+Error(1/Diet)
summary(aov(fit3, mydat))
```

- Not yet learned: To show Why Random model matters

```{r}
fit4 <- weight~Time+Error(Chick/Time)
summary(aov(fit4,mydat))
```


# Scheffe's Test
```{r}
library(agricolae)
mc.scheffe <- scheffe.test(aov(fit1,mydat), "Diet", group=FALSE, console=TRUE)
mc.scheffe$comparison
```

- So far, all the things are pairwise (Bonferoni?)
- Scheffe does multiple comparisons (between groups)
- More conservative than Bonferoni

```{r}
mc.bonf <- with(mydat, pairwise.t.test(weight, Diet, p.adj="bonf"))
mc.bonf
```

