Lab 5 (3/13)
========================================================

# Contrasts?

- This is an ANOVA thing. 
- Polynomial equation whose coefficents sum to 0.
- in ANOVA: a linear combination of factor level means whose coefficients sum to 0. "A weighted sum of the treatment means."

## Simple Example

- 2 means: $\mu_1, \mu_2$
- k levels: k-1 comparisons possible. 

## Orthogonal Contrasts

- if there are more than 2 comparisons, the pairwise product sum should be all 0. 

### Example.

- Treatments: T1, T2, T3 (control)
- Means: $\mu_1, \mu_2, \mu_3$
- ANOVA H0: all mus are same
- # of independent comparisons? df = 2
- Contrast hypotheses
  - Treatments different from control?
  - Treatments are different from each other?
- $L_a = 1\mu_1 + 0\mu_2 - 1\mu_3 = 0$
- $L_b = 0\mu_1 + 1\mu_2 - 1\mu_3 = 0$
- This is not orthogonal

## Regression Contrasts

- "Sum to Zero": ANOVA model in Regression form
- Criterion Y = $\beta_0 + \beta_1X_1 + \beta_2X_2 + \epsilon$
- $X_j$ = 1 or 0
- $\beta_0 = \mu_1 + \mu_2 + \mu_3/3$
- $\beta_1 = \mu_1 - (\mu_1 + \mu_2 + \mu_3)/3$
- $\beta_2 = \mu_2 - (\mu_1 + \mu_2 + \mu_3)/3$
- 1 fewer number of beta than listed

```{r}
y <- c(4,5,4,4,5,
       4,3,4,4,3,
       3,4,4,4,3)
group <- rep(letters[1:3], each=5)
dta <- data.frame(y=y, X=factor(group))
head(dta)

options(contrasts=c("contr.sum", "contr.poly"))
contrasts(dta$X)
model.matrix(y~X, dta)

contrast.joe <- matrix(NA,3,3)
contrast.joe[1,] <- 1/3  #intercept
contrast.joe[2,] <- c(-1,0,1)
contrast.joe[3,] <- c(0,-1,1)
contrast.joe

contrasts(dta$X) <- solve(contrast.joe)[,-1]
solve(contrast.joe)

fit2 <- lm(y~X, dta)
mus <- aggregate(y~X, dta, mean)[,2]
L.a <- contrast.joe

SSL <- sum(L.a*mus)^2/(sum(L.a^2)/5)
SSL/anova(fit2)["Residuals","Mean Sq"]
coef(summary(fit2))[,"t value"]^2
```

### Belows are the only thing that we need for HW4

```{r}
contrast.lee <- matrix(NA,3,3)
rownames(contrast.lee) <- c("GM", ":lv2", ":lv3")
contrast.lee[1,] <- 1/3
contrast.lee[2,] <- c(-1,1,0)
contrast.lee[3,] <- c(-1,0,1)
contrasts(dta$X) <- solve(contrast.lee)[,-1]
contrast.lee

solve(contrast.lee)[,-1]
```

### fit the model
```{r}
coef(summary(lm(y~X, dta)))
```

