Lab 6 (4/3)
========================================================

# Randomized block?
- Repeated measure - single person is a block.
- Subjects controlling variance themselves
- Concepts mostly coming from Kirk book.

# Randomized block RB-p
- ANOVA model: $Y_{ij} = \mu + \alpha_j + \pi_i + \epsilon_{ij}$
- $\mu = GM$
- $\alpha_j = \mu_{.j} - \mu$
- $\pi_i = \mu_{i.} - \mu$: the number of blocks (n). Random variable, normal distribution. 0 mean.
- $\epsilon_{ij} = Y_{ij} - \mu_{.j} - \mu_{i.} + \mu$

# SS's
- $SS_{total} = SS_A + SS_{Block} + SS_{RES}$
- $SS_{total} = [Y_{ij} - \bar{Y_{..}}]^2$

# Hypotheses
## Treatment A
- H0: $\alpha_j = 0 for all j$
- H1: not H0
- F = MS_a / MS_res = SSA/(p-1) / SSres/(n-1)(p-1)

## Block
- H0: $\alpha_{\pi}^2 = 0$
- H1: $\alpha_{\pi}^2 \neq 0$
- F = MS_block / MS_res = SS_block/(n-1) / ...

# Data
- 4 Altimeters
- Fixed. 
- Conceptually if fixed 
  - What's the level of drug's power
  - if random - Does it work?
  
```{r}
my.data <- read.csv("C:/Users/myeong/Desktop/alt.csv")
my.data
```

- If subj is number, it means something. It should be factor.

## Data format
```{r}
library(reshape2)
options(contrasts=c("contr.sum", "contr.poly")) #this gives a same result to SPSS, sum to 0.

my.data <- melt(my.data, id.vars="subj",
                variable.name="altimeter",
                value.name="readability") # aggregate all data to a single column.
head(my.data)

```

## Fit CR (Completely Randomized) Model
- No block anymore. $\pi$ part would be taken out.
- Don't care about subj.

### Fit
```{r}
mod.cr <- lm(readability~altimeter, my.data)

```

### ANOVA
```{r}
anova(mod.cr)
```

## Fit RB (Randomized Block) Model
- subj is regarded as error here.

### Fit
```{r}
my.data$subj <- factor(my.data$subj)
mod.rb <- lm(readability~altimeter+subj, my.data)
anova(mod.rb)
```

### ANOVA
```{r}
anova(mod.rb)
```

# Interaction?
```{r}
mod.full <- lm(readability~altimeter*subj, my.data)
anova(mod.full)
my.data
```

# Turkey's 1-df Test for Non-additivity
```{r}
library(asbio)
tukey.add.test(my.data$readability,
                my.data$subj,
                my.data$altimeter)
```

# Standard Errors
```{r}
dat <- read.csv("C:/Users/myeong/Desktop/alt.csv")
summary(dat)

# First reshape
dat1 <- melt(dat, id.var="subj")
summary(dat1)

#Boxplots are easy/informative
require(ggplot2)
qplot(variable, value, data= dat1, geom="boxplot") + theme_classic(base_size=24)

#Second reshape
require(plyr)
dat2 <- ddply(dat1, .(variable), summarise, means = mean(value), 
              ses = sd(value)/sqrt(length(value)))  #standard errors
summary(dat2)

#Error bars are also appropriate
qplot(variable, means, data = dat2, size =2) +
  geom_errorbar(aes(ymin=means - ses, ymax=means + ses), width=.5, size=1 ) +
  theme_classic(base_size=24)

#Other interesting possibilities, called spagetti plot
qplot(variable, value, data = dat1, geom="boxplot") +
  geom_line(aes(color = factor(subj), group = factor(subj)), size=1.5 ) +
  theme_classic(base_size=24)

```

