Homework 4 (3/27)
========================================================

Myeong Lee
--------------------------------------------------------

```{r}
options(contrasts = c("contr.sum", "contr.poly"))
data1 <- read.csv("C:/Users/myeong/Desktop/hw4.csv")

my.dat <- data1[,c("y", "Group")]
my.dat$Group <- factor(my.dat$Group, levels = c(1,2,3,4))
my.dat
```

# Part I

### 1. Model
- Y = $\beta_0 + \beta_1X_1 + \beta_2X_2 + \beta_3X_3 + \epsilon$

### 2. H0

- $H_0: \beta_1 = \beta_2 = \beta_3 = 0$ or $\mu_1 = \mu_2 = \mu_3 = \mu_4$
- There is no systematic difference among the group means. All the groups have same means. 

### 3. H1

- $H_1: \beta_j \neq 0$, $Not H_0$
- There are systematic differences among group means. 

### 4. Error Rate $\alpha$

- at $\alpha = 0.05$, critical t(2)=4.30
- actual $\alpha$ = 1 - $0.95^3$ = .142625
- $\frac{.142625}{4}$ = .0356 < .0.05
- So, alpha can be set as $\alpha = P(P|H_0) = 0.05$ 
  
### 5. Regression form
```{r}
fit1 <- lm(y~Group, my.dat)
coef(summary(fit1))
```

### 6. One Predictor
```{r}
fit0 <- lm(y~1, my.dat)
coef(summary(fit0))

anova(fit0, fit1)

```
- The model that includes the categorical is better, since P-value shows that it rejects the null hypothesis in the significance level 0.05.

### 7. Plot
```{r}
my.dat$e <- residuals(fit1)
my.dat$y.hat <- fitted(fit1)
frame1 <- data.frame(y=my.dat$y, y_hat=my.dat$y.hat, e=my.dat$e, X=my.dat$Group)

library(GGally)

ggpairs(frame1, lower=list(continuous="smooth"))

```

### 8. Data frame
```{r}
frame1
```

### 9. Correlation
```{r, results='asis'}
library(xtable)
frame2 <- data.frame(y=my.dat$y, y_hat=my.dat$y.hat, e=my.dat$e)
my.cor <- cor(frame2)
print(xtable(my.cor), type="html")

```

### 10, 11. Explanation
- The data are not that systematically differentiated between groups. y and y_hat are correlated, while y and e are also highly correlated: cannot be said that samples are systematically differentiated. 


# Part II
```{r}
contrasts(my.dat$Group)
model.matrix(y~Group, my.dat)

contrast.lee <- matrix(NA,4,4)
rownames(contrast.lee) <- c("GM", ":12v34", ":2v3", ":1v4")
contrast.lee[1,] <- 1/4
contrast.lee[2,] <- c(-1,-1,1,1)
contrast.lee[3,] <- c(0,-1,1,1)
contrast.lee[4,] <- c(-1,0,0,1)
contrasts(my.dat$Group) <- solve(contrast.lee)[,-1]
contrast.lee

solve(contrast.lee)

fit2 <- lm(y ~ Group, my.dat)
mus <- aggregate(y ~ Group, my.dat, mean)[, 2]
L.a <- contrast.lee

SSL <- sum(L.a * mus)^2/(sum(L.a^2)/5)
SSL/anova(fit2)["Residuals", "Mean Sq"]

coef(summary(fit2))[, "t value"]^2
```

- I am not sure how to set the contrast matrix...

# Part III
```{r}
contrasts(my.dat$Group) <- cbind(":12v34" = c(-1,-1,1,1),
                                ":1v4" = c(-1,0,0,1),
                                ":2v3" = c(0,-1,1,0))
cbind(":12v34" = c(-1,-1,1,1),":1v4" = c(-1,0,0,1),":2v3" = c(0,-1,1,0))
fit3 <- lm(y ~ Group, my.dat)
mus <- aggregate(y ~ Group, my.dat, mean)[, 2]
L.a <- contrast.lee

SSL <- sum(L.a * mus)^2/(sum(L.a^2)/5)
SSL/anova(fit3)["Residuals", "Mean Sq"]

coef(summary(fit3))[, "t value"]^2
```

- The result shows that the treatment 1 and 2 are systematically different from the controls (3 and 4).
