Homework 1
========================================================

Myeong Lee
--------------------------------------------------------
  
### Task 1
  
##### H0 in formal expression

$\rho = \frac{\sum(z_y Z_X)}{N} = 0$

##### H0 in words expression
- There is no relationship between X and y in the population. Any difference from zero found in the sample is due to chance or random factors.


### Task 2
  
##### H1 in formal expression
$\rho = \frac{\sum(z_y Z_X)}{N} \neq 0$

##### H1 in words expression
- There is a positive or negative relationship between X and y in the population. 


### Task 3: Margin of error $\alpha$
```{r}
data1 <- read.csv("C:/Users/myeong/Desktop/hw1.csv")
data1
rz.ci <- function(N, conf.level = 0.95){
  zr.se <- 1/(N - 3)^0.5
  moe <- qnorm(1 - (1 - conf.level)/2) * zr.se  
}

rz.ci(nrow(data1), 0.95)[1]
```


### Task 4: Regression
```{r}
fit1 <- lm(y~X, data=data1)
summary(fit1)

fit2 <- update(fit1, scale(y)~scale(X))
summary(fit2)
```


### Task 5: Raw-score and the Standardized Prediction Equation

##### Raw-score Prediction Equation

- Y = 15.286 + 4.179X + e

##### Standardized Prediction Equation

- Y = 0.968X  


### Task 6: Time-series plots of y and e

##### y - observation number
```{r}
library(ggplot2)
data1$e <- residuals(fit1)
data1$y.hat <- fitted(fit1)

qplot(1:nrow(data1), y, data=data1, main="Time Series - y", xlab="Obs #", ylab="Values")

```

##### e - observation number
```{r}
qplot(1:nrow(data1), e, data=data1, main="Time Series - e", xlab="Obs #", ylab="residuals")

```


### Task 7: data.frame with y, X, y_hat, and e for each observation

```{r}
frame1 <- data.frame(y=data1$y, X=data1$X, y_hat=data1$y.hat, e=data1$e)
frame1
```


### Task 8: Correlations
```{r, results='asis'}
library(xtable)

my.cor <- cor(data1)
print(xtable(my.cor), type="html")

```

### Task 9: Pairwise scatter plots and correlations
```{r}
library(GGally)

ggpairs(data1, lower=list(continuous="smooth"))

```

### Task 10: Intercorrelations found

- y and X are closely, positively correlated with the coeff 0.97.
- y and e are loosely correlated with the coeff 0.25.
- y.hat and y are very closely correlated (coeff 0.968) since the error is very small in this regression.
- X and y.hat are perfectly correlated since they are predicted values.
- X and e are not correlated (coeff=0) by definition.
- e and y.hat are not correlated by definition.

### Task 11: Interpret the Results

```{r}
anova(fit1)
```
- In the hypothesis test, F-value is 73.835 and the significance level is very high, satisfying 0.04% significance level. 


