Homework 3
========================================================

Myeong Lee
--------------------------------------------------------

```{r}
options(contrasts = c("contr.sum", "contr.poly"))
data1 <- read.csv("C:/Users/myeong/Desktop/hw3.csv")

my.dat <- data1[,c("y", "Group")]
my.dat$Group <- factor(my.dat$Group, levels = c(1,2,3,4))

```


## Part I

### 1. The model under investigation

$y_{i(j)} = \mu + \alpha_j + \varepsilon_{i(j)}$

### 2. H0

- $H_0: \alpha_j = 0$, $n\sigma_M^2 = \sigma^2$

- There is no systematic difference among the group means. All the groups have same means. 

### 3. H1

- $H_1: \alpha_j \neq 0$, $n\sigma_M^2 > \sigma^2$
  
- There are systematic differences among group means. 

### 4. Error Rate $\alpha$

- at $\alpha = 0.05$, critical t(2)=4.30
- actual $\alpha$ = 1 - $0.95^3$ = .142625
- $\frac{.142625}{4}$ = .0356 < .0.05
- So, alpha can be set as $\alpha = P(P|H_0) = 0.05$ 
  
### 5. ANOVA 

##### Fixed model
```{r}
fit1 <- y~Group
summary(aov(fit1, my.dat))
```

```{r}
fit1.1 <- lm(y ~ Group, data=my.dat)
summary(fit1.1)
```

```{r}
anova(fit1.1)
```


##### Random model
```{r}
fit2 <- y~Error(Group)
summary(aov(fit2, my.dat))
```

### 6. Plot

##### y - observation number
```{r}
library(ggplot2)
my.dat$e <- residuals(fit1.1)
my.dat$y.hat <- fitted(fit1.1)

qplot(1:nrow(my.dat), y, data=my.dat, main="Time Series - y", xlab="Obs #", ylab="Values")

```

##### e - observation number
```{r}
qplot(1:nrow(my.dat), e, data=my.dat, main="Time Series - e", xlab="Obs #", ylab="residuals")

```


### 7. Data frame
```{r}
frame1 <- data.frame(y=my.dat$y, y_hat=my.dat$y.hat, e=my.dat$e)
frame1
```

### 8. Correlations

```{r, results='asis'}
library(xtable)

my.cor <- cor(frame1)
print(xtable(my.cor), type="html")

```

### 9. Pairwise plots
```{r}
library(GGally)

ggpairs(frame1, lower=list(continuous="smooth"))

```

### 10. Plot of the mean of y

```{r}
sub1 <- subset(my.dat, Group==1)
sub1.mean <- mean(sub1$y)

sub2 <- subset(my.dat, Group==2)
sub2.mean <- mean(sub2$y)

sub3 <- subset(my.dat, Group==3)
sub3.mean <- mean(sub3$y)

sub4 <- subset(my.dat, Group==4)
sub4.mean <- mean(sub4$y)

subtable <- data.frame(y=c(sub1.mean, sub2.mean, sub3.mean, sub4.mean), Group=c(1,2,3,4))

qplot(1:nrow(subtable), y, data=subtable, main="Means of y", xlab="Group Membership Variable", ylab="Mean of y")

```

### 13. Interpretation

- Since F value is 4 on df(3,12) and p-value is .035, it rejects null hypothesis at $\alpha$= .05, but the significance is not that high.


## Part II

### 1. What is it?
- Compare each group to determine whether they are systematically differ, and to determine $\alpha$

### 2. Bonferroni

```{r}
mc.bonf <- with(my.dat, pairwise.t.test(y, Group, p.adj="bonf"))
mc.bonf
```

### 3. Scheffe's

```{r}
library(agricolae)
mc.scheffe <- scheffe.test(aov(fit1, my.dat), "Group", group=FALSE, console=TRUE)
mc.scheffe$comparison
```


### 4. Benefits

- Through Banferroni and Scheffe's test, I can see which groups are not different from each other. Since Scheffe's tests all possible pairs, it is good to see the differences. 


### 5. Difference between the two tests

- Scheffe's test is more conservative since it does multiple comparisons while Bonferroni does pairwise comparisons.

### 6. More interpretation

- Group 1 and 3 are somewhat systematically different, but other groups are not different that much (in a systematic manner). Significance levels are not that high.